\bf Adaption of the Chumbley Score to matching of bullet striation marks

### 2018-03-18 doc/paper.Rmd
profile signature

```{r win-comparison, fig.width=8, fig.height=5, out.width='\\textwidth', fig.cap=" The two plots on the left show how the same shift behaves in case of a matching pair and the two plots on the right show how the different shift behaves in case of a matching pair."}

@@

Neither of above sets of correlation in the two sub-steps are allowed to include the maximum correlation window as identified earlier. Therefore the assumption is that if two markings match each other, the same-shift correlations would be larger than the different-shift windows.
And if they are not a match the correlations in the two sets will be very similar. The U-statistic tests for the null hypothesis that the two markings are not a match and are therefore not made by the same source.  As given by \citet{hadler}, it is computed from the joint rank of all correlations of both the same and different shift samples. 
-->

##################

@@

- scans available: NIST database (citation), Hamby 44 and Hamby 252 (Hamby citation)
- move figure up
- discuss cross section, profiles and signatures

@@

# Simulation setup

>>>>

```{r win-comparison, warning=FALSE, fig.width=8, fig.height=3.5, fig.cap="Two markings made by the same source. For convenience, the markings are moved into phase on the left and out-of phase on the right. In-phase (left) and out-of-phase (right) samples are shown by the light grey background. The Chumbley-score is based on a Mann-Whitney U test of the correlations derived from these two sets of samples."}
sigs_graphics <- readRDS("../data/sigs_generate_window.rds")
sigs_graphics$sigs_land_id_1_match <- sigs_graphics$sigs_land_id_1_match %>% group_by(land_id) %>% mutate(y = y-min(y, na.rm=T))

# Matching signature
d1<- sigs_graphics.match[which(sigs_graphics.match$land_id==1,arr.ind = TRUE),]
d2<- sigs_graphics.match[which(sigs_graphics.match$land_id==276,arr.ind = TRUE),]
data1<-d1 %>%select(l30)
#data1<- data1$y
data2<- d2 %>%select(l30)
#data2<- data2$y
window_opt = 120 
window_val = 50
coarse = 1
data1<- matrix(unlist(data1))
data2<- matrix(unlist(data2))

sigs1.min = sigs_graphics[[1]] %>% filter(land_id==1) %>% select(y) %>% min()
sigs2.min = sigs_graphics[[1]] %>% filter(land_id==276) %>% select(y) %>% min()
window_val <- 3*window_val*0.645

same.shift <- -(365-338)*1/.645 + sigs2.min - sigs1.min 
xs <- seq(100, 1800, length=10)
rects <- data.frame(ymin=-Inf, ymax= Inf, xmin = xs, xmax = xs+window_val)

p1 <- sigs_graphics[[1]] %>% filter(land_id %in% c(1, 276)) %>% 
  ggplot() + 
  geom_segment(aes(x = xmin, y=ymin, xend = xmin, yend=ymax), 
               colour="grey50", linetype=3, data = rects) +
  geom_segment(aes(x = xmax, y=ymin, xend = xmax, yend=ymax), 
               colour="grey50", linetype=3, data = rects) +
  geom_rect(aes(xmin=xmin, xmax=xmax, ymin=ymin, ymax=ymax), 
            data=rects, fill= "grey90") +
  geom_line(aes(x = y-same.shift*I(land_id==276), 
                y=l30-5*I(land_id==276), group=land_id)) + 
  theme_bw() +
  theme(axis.title.y = element_blank(), 
        axis.text.y = element_blank(),
        axis.ticks.y = element_blank()) +
  xlab(expression(paste("Relative Location (in ",mu,m,")", sep=""))) + 
  ggtitle("In-phase sample")

diff.shift <- -(365-338)*1/.645 + sigs2.min - sigs1.min + 70

p2 <- sigs_graphics[[1]] %>% filter(land_id %in% c(1, 276)) %>% 
  ggplot() + 
  geom_segment(aes(x = xmin, y=ymin, xend = xmin, yend=ymax), 
               colour="grey50", linetype=3, data = rects) +
  geom_segment(aes(x = xmax, y=ymin, xend = xmax, yend=ymax), 
               colour="grey50", linetype=3, data = rects) +
  geom_rect(aes(xmin=xmin, xmax=xmax, ymin=ymin, ymax=ymax), 
            data=rects, fill= "grey90") +
  geom_line(aes(x = y-diff.shift*I(land_id==276), 
                y=l30-5*I(land_id==276), group=land_id)) + 
  theme_bw() +
  theme(axis.title.y = element_blank(), 
        axis.text.y = element_blank(),
        axis.ticks.y = element_blank()) +
  xlab(expression(paste("Relative Location (in ",mu,m,")", sep=""))) + 
  ggtitle("Out-of-phase sample")

library(gridExtra)
grid.arrange(p1,p2, ncol=2)
```

```{r win-comparison-2, fig.width=8, fig.height=5, out.width='\\textwidth', fig.cap=" The two plots on the left show how the same shift behaves in case of a matching pair and the two plots on the right show how the different shift behaves in case of a matching pair.", eval=FALSE}

@@

Neither of above sets of correlation in the two sub-steps are allowed to include the maximum correlation window as identified earlier. Therefore the assumption is that if two markings match each other, the same-shift correlations would be larger than the different-shift windows.
And if they are not a match the correlations in the two sets will be very similar. The U-statistic tests for the null hypothesis that the two markings are not a match and are therefore not made by the same source.  As given by \citet{hadler}, it is computed from the joint rank of all correlations of both the same and different shift samples. 
-->
<!--
##################

@@

- scans available: NIST database (citation), Hamby 44 and Hamby 252 (Hamby citation)
- move figure up
- discuss cross section, profiles and signatures
-->

@@

# Testing setup

## The Data

\hh{More on NIST database, some on CSAFE}

\hh{Introduce profiles and signatures, as shown in figure \ref{fig:sigs-profiles}.}

```{r sigs-profiles, fig.width = 8, fig.height = 2.5, fig.cap="Bullet land profile (left) and the corresponding signature (right)."}
p1 <- sigs_graphics[[1]] %>% filter(land_id==19) %>%
  ggplot(aes(x = y, y = value)) + geom_line() +
  theme_bw() +
  ylab(expression(paste("Depth (in ",mu,m,")", sep=""))) + 
  xlab(expression(paste("Relative Location (in ",mu,m,")", sep=""))) + 
  ggtitle("Profile")

p2 <- sigs_graphics[[1]] %>% filter(land_id==19) %>%
  ggplot(aes(x = y, y = l30)) + 
  geom_line(aes(y=resid), size=.25) +
  geom_line(aes(y=l30)) +
  theme_bw() +
  ylab(expression(paste("Depth (in ",mu,m,")", sep=""))) + 
  xlab(expression(paste("Relative Location (in ",mu,m,")", sep=""))) + 
  ggtitle("Signature")

grid.arrange(p1,p2, ncol=2)
```

## Setup

\hh{using (a) signatures and (b) profiles, run chumbley score across scans from NIST and CSAFE for various settings of $w_o$ and $w_v$ (and coarseness $c$ for profiles).}

## Results

### 2018-03-18 doc/paper.tex
change of figure 2
profile signature

\caption{In- and out-of-phase samples from two markings created by the same source. On the left, sample windows are in-phase, on the right the pairs of sampled windows are out-of-phase. The Chumbley-score is based on a Mann-Whitney U test of the correlations derived from these two sets.}\label{fig:win-comparison}
\end{figure}

@@

\paragraph{endedit}\label{endedit}

\hh{end of intro: remaining paper is structured as follows: introduce to the data we get from confocal microscopy, introduce to profiles and signatures.
Introduce to chumbley score method, apply chumbley and discuss results ....
}

\subsection{Scans for land engraved
areas}\label{scans-for-land-engraved-areas-1}

\begin{itemize}
\tightlist
\item
  scans available: NIST database (citation), Hamby 44 and Hamby 252
  (Hamby citation)
\item
  move figure up
\item
  discuss cross section, profiles and signatures
\end{itemize}

\section{Simulation setup}\label{simulation-setup}

@@

\section{Results}\label{results}

>>>>

\caption{Two markings made by the same source. For convenience, the markings are moved into phase on the left and out-of phase on the right. In-phase (left) and out-of-phase (right) samples are shown by the light grey background. The Chumbley-score is based on a Mann-Whitney U test of the correlations derived from these two sets of samples.}\label{fig:win-comparison}
\end{figure}

@@

\section{Testing setup}\label{testing-setup}

\subsection{The Data}\label{the-data}

\hh{More on NIST database, some on CSAFE}

\hh{Introduce profiles and signatures, as shown in figure \ref{fig:sigs-profiles}.}

{\centering \includegraphics[width=\textwidth]{figures/sigs-profiles-1}

\caption{Bullet land profile (left) and the corresponding signature (right).}\label{fig:sigs-profiles}
\end{figure}

\subsection{Setup}\label{setup}

\hh{using (a) signatures and (b) profiles, run chumbley score across scans from NIST and CSAFE for various settings of $w_o$ and $w_v$ (and coarseness $c$ for profiles).}

\subsection{Results}\label{results}

@@

\section{Results}\label{results-1}
